Factoring with $n+2$ clean qubits and $n-1$ dirty qubits

### 2017-05-12 doc/paper.tex
Rewrote rewrote rewrote conclusion

\section{Conclusion} \label{sec:conclusion}

We presented Toffoli-based arithmetic circuits that reduce the smallest known number of qubits required to perform Shor's algorithm by 1, and allowed an additional $n-1$ qubits to be dirty.

>>>>

\section{Future Work and Conclusion} \label{sec:conclusion}

Of the $2n+1$ qubits our period-finding construction requires: $1$ is used for the phase estimation qubit, $n$ are used to store the work register, and $n$ are ancilla used to implement modular multiplication in terms of scaled modular addition.
All the other constructions, for simpler arithmetic, need two or fewer dirty ancilla.
Furthermore, because scaled modular addition is reduced into operations that have a $\Theta(n)$ surplus of unused qubits, in context there's always more than enough dirty ancilla available to implement the simpler arithmetic inline.
There's so much slack in the simpler arithmetic constructions that improving the number of qubits used by period-finding effectively means improving the very first step, from multiplication to some other operation, and nothing else.

For example, consider a situation where we could cut multiplication operations into two pieces.
If we knew the factorization $p \cdot q$ of the modulus $R$, with $p$ and $q$ each having size $\approx n/2$, then the Chinese remainder theorem guarantees we could uniquely represent $x \mod R$ as the pair $(x \mod p, x \mod q)$.
Multiplications of the half-sized values could use and re-use the same half-sized clean ancilla register, so there would be three half-sized registers (one for $x \mod p$, one for $x \mod q$, and one ancilla register) for a total qubit count of $\approx 1.5n$.
Despite the large reduction in the number of ancilla available to them, the underlying constructions would still contribute no additional ancilla.
(Note: because the initial value $x_0 = 1$ is trivial, and the final value is discarded, it's not necessary to implement circuits that translate between the Chinese-remainder representation and the usual 2s-complement representation.)
Of course, since we use period-finding to compute the factorization of $R$, using the factorization of $R$ to optimize period-finding would be paradoxical.

We presented Toffoli-based arithmetic circuits that reduce the smallest known number of qubits required to perform Shor's algorithm from $2n+2$ to $2n+1$.
The constructions also reduce the number of {\em clean} qubits required by $n$, so the number of clean qubits required is now $n + O(1)$.
We consider this to be a step towards a period-finding construction that uses only $n + O(1)$ qubits total, which could reduce the expected lifetime of current cryptographic keys by months or years (depending on how quickly quantum computers gain error-corrected capacity).
